\documentclass[11pt]{article}
\usepackage{parskip} % gets rid of indenting, increases paragraph spacing
\usepackage{outlines} % used for course outline

\begin{document}

\begin{center}
\section*{Computational Financial Risk}
{\bf MATH 5xx, Fall 2019}
\end{center}

\vspace{3mm}
\hrule
\vspace{3mm}

\textsc{Instructor:} Pete Benson (pbenson@umich.edu),  2082C East Hall

\textsc{Office Hours:} 10:00am-12:00pm Mondays, Wednesdays, or by appointment. Group appointments are encouraged.

\textsc{Web page:}  See Canvas for all course details.

\textsc{Texts:}  I will reference the following. Purchasing the texts is not essential. 
\begin{itemize}
	\item Allan M. Malz, {\it Financial Risk Management: Models, History, and Institutions}, 2010. Available online via https://search.lib.umich.edu.
	\item John C. Hull, {\it Risk Management And Financial Institutions}, 2015. Edition to be decided. 
	\item Mina and Xiao, {\it Return to RiskMetrics: The Evolution of a Standard}, 2001. Available via download on Canvas.
	\item Yves Hipisch, {\it Python for Finance: Analyze Big Financial Data}.
\end{itemize}

\textsc{Grading:}  
\begin{itemize}
	\item in class assignments (10\%). Two lowest scores will be dropped. 
	\item Homework problems (20\%). You can discuss with others, but write and submit your own work. 
	\item Python and Java programs (30\%). You can work together on these. Grades will be based on brief one-on-one code in-class reviews with instructor. 
	\item midterm exam (20\%)
	\item final exam (20\%)
\end{itemize}


\textsc{Prerequisites:}
The equivalent of Math 423 (Mathematics of Finance), Math 425 (Introduction to Probability), a programming course (e.g. EECS 183)

\textsc{Synopsis:} This course emphasizes understanding and implementing risk models using Python and Java, both of which have widespread use in finance. The style of the course is While the programming prerequisites are minimal, during the course you should be prepared to develop fluency with the pandas and numpy libraries of Python, and object-oriented design in both languages. By the end, you will be well-prepared to interview for a quantitative role in risk management.

Expect to spend a portion of class time working in small groups. Everyone will be asked to on occasion to present their group's work to the class. This will give you practice in collaborating and communicating in financial language.

\textsc{Course Outline} 

\begin{outline}[enumerate]
\1 History of risk management and mismanagement
	\2 Regulatory environment, economic and regulatory capital
	\2 Investor environment
\1 Object-oriented modeling of markets and portfolios
\1 Modeling portfolio P\&L 
	\2 Variance-covariance (Markowitz)
	\2 Historical and Monte Carlo simulation 
\1 Risk Measures
	\2 Standard deviation, VaR, Expected shortfall
	\2 Risk attribution
	\2 Coherent risk measures
\1 Credit Risk
	\2 CreditMetrics
	\2 Basket securities such as CDOs 
\1 Credit Valuation Adjustment (CVA)
\1 Stress Testing
\end{outline}

\textsc{Academic integrity}:  Academic Integrity:
The LSA undergraduate academic community, like all communities, func- tions best when its members treat one another with honesty, fairness, re- spect, and trust. The College holds all members of its community to high standards of scholarship and integrity. To accomplish its mission of provid- ing an optimal educational environment and developing leaders of society, the College promotes the assumption of personal responsibility and integrity and prohibits all forms of academic dishonesty and misconduct. Academic dishonesty may be understood as any action or attempted action that may result in creating an unfair academic advantage for oneself or an unfair aca- demic advantage or disadvantage for any other member or members of the academic community. Conduct, without regard to motive, that violates the
academic integrity and ethical standards of the College community cannot be tolerated. The College seeks vigorously to achieve compliance with its community standards of academic integrity. Violations of the standards will not be tolerated and will result in serious consequences and disciplinary action.

\end{document}